%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape David Dao} \\ \vspace{1pt}
    \small 949-445-2278 $|$ \href{mailto:x@x.com}{\underline{davidvd@uci.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/david-v-dao}} $|$
    \href{https://github.com/...}{\underline{github.com/david-dao28}} $|$
    \small Aliso Viejo, CA
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Irvine}{Irvine, CA}
      {Bachelor of Science in Computer Science}{Sep. 2020 -- Dec. 2023}
      \resumeItemListStart
        \resumeItem{GPA: 3.96}
        \resumeItem{Relevant Coursework: HCI, User Interface Software, Relational Databases and Web Applications,
        Non-Relational Databases, Information Retrieval, Programming in Python and Java, ML \& Data Mining }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{June -- Sep. 2022, June -- Sep. 2023}
      {Johns Hopkins Applied Physics Laboratory}{Laurel, MD}
      \resumeItemListStart
        \resumeItem{Delivered Angular-based front-end features for a web application under tight deadlines by swiftly translating requirements and undergoing the Software Development Life Cycle.}
        \resumeItem{Transformed a PostgreSQL database schema to enhance the visibility of the system's status, employing proper techniques for concurrency and maintaining data consistency.}
        \resumeItem{Expedited an analyst's workflow for annotating documents by implementing a text similarity algorithm (cosine similarity) that groups/collapses near-duplicate documents together.}
        \resumeItem{Contributed to a web framework using JS/HTML/CSS that helps AI projects select tools specific to its needs and are deemed responsible by a set of ethical principles laid out by the Department of Defense. }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{ZotWee} $|$ \emph{Google Directions API, BeautifulSoup, HTML/CSS/JavaScript}}{Nov. 2023}
      \resumeItemListStart
        \resumeItem{Mentored a team over a 12-hour hackathon to create a web application that navigates UCI students to the nearest gender-neutral and ADA-compliant restrooms on campus.}
        \resumeItem{Placed 1st out of 20 teams in ZotHacks, UCI's annual, beginner-friendly hackathon.}
      \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{ZotGainz} $|$ \emph{Twilio API, BestTime API, React Native, Firebase, Figma}}{Feb. 2023 - Present}
      \resumeItemListStart
        \resumeItem{Creating a mobile application that serves as a gym utility tool for UC Irvine students.}
        \resumeItem{Won First Place for "Best Use of Twilio API" at Hack UCI, Orange County's largest collegiate hackathon.}
        \resumeItem{Using React Native and Twilio’s SMS API to build the mobile user interface and push text messages to users upon making a reservation.}
        \resumeItem{Measured the gym’s expected “busyness” throughout the week by using foot traffic data retrieved with the BestTime API.            }
        \resumeItem{Collaborating with campus clubs to iteratively enhance the app's features with a community-centric approach.}
      \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{ZotBins} $|$ \emph{React Native, Firebase, Express.js, Node.js}}{Oct. 2021 - Present}
          \resumeItemListStart
            \resumeItem{Creating a mobile application using React Native that spreads awareness on sustainability and zero-waste practices at UCI.}
            \resumeItem{Independently created a RESTful API connected to our NoSQL database, Firebase Firestore, using Node.js and Express.js.}
            \resumeItem{Leading weekly team meetings to delegate tasks and foster creative ideation for app’s features.}
            \resumeItem{Pitched our project to a panel of judges to win \$1000 in the UCI Sustainability Challenge.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Spotflix} $|$ \emph{Spotify Web API, Java, Javascript, HTML/CSS, MySQL }}{Apr. 2023 -- June 2023}
          \resumeItemListStart
            \resumeItem{Co-developed with a partner a full-stack web application that enables Spotify users to browse and filter through their top songs, artists, and genres.}
            \resumeItem{Utilized the Microservices architecture on AWS, leveraging Java servlets and JDBC to establish connectivity with a MySQL data source.}
            \resumeItem{Increased scalability and security through the implementation of reCAPTCHA, cookies, connection pooling, and load balancing using master-slave instances.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, SQL (MySQL, Postgres), Javascript, Typescipt, HTML/CSS} \\
     \textbf{Frameworks/Libraries}{: React/React Native, Angular, Node.js, Express, JUnit, pandas, NumPy, scikit-learn} \\
     \textbf{Developer Tools}{: Git, GitLab, Docker, Google Cloud Platform, AWS, Android Studio, IntelliJ, Jira, Figma, Jupyter Notebook} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}